Low-Cost Data Deduplication for Virtual Machine Backup in Cloud Storage

### 2013-11-25 batchdedup/eval.tex
added dual bin packing text back into paper. Added figures comparing jobspan and avg backup time

>>>>

\todo{The names of the algorithms are just the temporary names I've been using for coding, DBP2 is the relative of the dual bin packing algorithm, BPL is the machine by machine largest VM to shortest round algorithm}
\begin{figure}[ht]
  \centering
	\begin{tikzpicture}
		\begin{axis}[
		%title={Network Buffer Size},
		xlabel={Rounds},
		ylabel={Total Jobspan (s)},
		%extra y ticks={4.5,5.5,6.5} %to show extra ticks
                %legend pos=north west
		]
                \addplot table[x=Rounds,y=DBP2jobspan] {figures/packing_comparison.txt};
                \addplot table[x=Rounds,y=BPLjobspan] {figures/packing_comparison.txt};
                \legend{DBP2, BPL};
		\end{axis}
	\end{tikzpicture}
  \caption{Jobspan for DBP2 and BPL}
  \label{fig:jobspan-comparison}
\end{figure}

\begin{figure}[ht]
  \centering
	\begin{tikzpicture}
		\begin{axis}[
		%title={Network Buffer Size},
		xlabel={Rounds},
		ylabel={Average Backup Time (s)},
		%extra y ticks={4.5,5.5,6.5} %to show extra ticks
                %legend pos=north west
		]
                \addplot table[x=Rounds,y=DBP2avgbackup] {figures/packing_comparison.txt};
                \addplot table[x=Rounds,y=BPLavgbackup] {figures/packing_comparison.txt};
                \legend{DBP2, BPL};
		\end{axis}
	\end{tikzpicture}
  \caption{Average Backup Time for DBP2 and BPL}
  \label{fig:avgbackup-comparison}
\end{figure}
